### 2016-03-23 docs/ms_communitySynchrony.Rmd
adds main text word count and tex file

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \usepackage{todonotes}
   - \doublespacing
   - \usepackage{color}
   - \usepackage{rotating}
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: false
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
---

@@

\textbf{Number of Words}: Abstract = ; Main Text =

>>>>

---
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl
fontsize: 12pt
geometry: margin=1in
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{setspace}
- \usepackage{todonotes}
- \doublespacing
- \usepackage{color}
- \usepackage{rotating}
layout: 12pt
linkcolor: black
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  word_document: default
urlcolor: black
---

@@

\textbf{Number of Words}: Abstract = 138; Main Text = 4929 (including section titles and in-line citations)
